Continuous Deductive Reasoning over Streamed RDF Data

### 2015-12-02 article.tex

  \begin{figure*}[t]
    \centering
    \begin{ebnf}
      \Rule{Document}{
              \Optional{\NTerm{IRIMETA}} 
              \Token{Document} 
              \Token{(} 
              \Optional{\NTerm{Base}} 
              \ZeroOrMore{\NTerm{Prefix}} 
              \ZeroOrMore{\NTerm{Import}}
              \Optional{\NTerm{Window}}
              \Optional{\NTerm{Group}} 
              \Token{)}
      }
      \Rule{Base}{
              \Token{Base} 
              \Token{(} 
              \NTerm{ANGLEBRACKIRI} 
              \Token{)}
      }
      \Rule{Prefix}{
              \Token{Prefix} 
              \Token{(} 
              \NTerm{Name} 
              \NTerm{ANGLEBRACKIRI} \Token{)}
      }
      \Rule{Import}{
              \Optional{\NTerm{IRIMETA}} 
              \Token{Import} 
              \Token{(} 
              \NTerm{LOCATOR} 
              \Optional{\NTerm{PROFILE}} 
              \Token{)}
      }
      \Rule{Group}{
              \Optional{\NTerm{IRIMETA}} 
              \Token{Group} 
              \Token{(} 
              \ZeroOrMore{\OrList{\NTerm{RULE} \OrSep \NTerm{Group}}} 
              \Token{)}
      }
      \Rule{RULE}{
              \Optional{\NTerm{IRIMETA}}
              \Token{Forall}
              \OneOrMore{\NTerm{Variable}}
              \Token{(}
              \NTerm{CLAUSE}
              \Token{)}
      }
      \OrRule{
              \NTerm{CLAUSE}
      }
      \Rule{CLAUSE}{
              \OrList{\NTerm{Implies} \OrSep \NTerm{ATOMIC}}
      }
      \Rule{Implies}{
              \Optional{\NTerm{IRIMETA}}
              \OrList{\NTerm{ATOMIC} \OrSep \Token{And} \Token{(} \ZeroOrMore{ATOMIC} \Token{)}}
              \Token{:-}
              \NTerm{FORMULA}
      }
      \Rule{LOCATOR}{
              \NTerm{ANGLEBRACKURI}
      }
      \Rule{PROFILE}{
              \NTerm{ANGLEBRACKURI} 
      }
      \Rule{Window}{
              \NTerm{Number}
              \NTerm{TimeUnit}
      }
      \Rule{TimeUnit}{
              \OrList{\Token{ms} \OrSep \Token{s} \OrSep \Token{m} \OrSep \Token{h}}
      }
    \end{ebnf}
    \caption{Streaming RIF-Core Grammar}
    \labelfig{lst-S-RIF-Core}
  \end{figure*}

  A rule document containing any number of rules is submitted to the system.
  We have chosen RIF-Core to be the language in which rules can be represented, for being compatible with RDF and other semantic web standards, as well as sharing the semantics of positive Datalog.
  The rule document specifies any domain-specific rules as well as an entailment regime \emph{if any} for background reasoning.
  We also added a simple extension to RIF-Core in line with the extension of Datalog described in \refsec{semantics}, enabling users to specify a window range as part of their rule set, as shown in \reffig{lst-S-RIF-Core}.
  Further, we propose the extension of the set of `PROFILE's that describe the `Import's of a rule set to include those definitions of RDF streams recognised by the W3C.

@@

\begin{nestedsection}{Evaluation, Results and Discussion}{evaluation}
  To evaluate the performance of R4, we compare it with state-of-the-art systems that provide the capability of performing background reasoning to some extent on streamed semantic data.
  These include Etalis \citep{EP-SPARQL}, Sparkwave \citep{sparkwave}, Streaming knowledge bases \citep{walavalkar08streamingkb}, and the incremental reasoner presented in \citep{inc-reasoning-background-knowledge}.
  To the best of our knowledge, the latter two implementations were never made public, so we compare R4 against Etalis and Sparkwave only.
  The experiments are performed on an Intel Core i5 computer with 3.2 GHz and 8 GB memory.
  We set up Jtalis (the Java wrapper of Etalis) over SWI-Prolog v7.2.1 and installed Sparkwave v0.5.1.

  \begin{nestedsection}{Comparative Results}{evaluation: comparative results}
    \begin{figure*}[t]
      \centering
      \begin{verbatim}
Forall ?offer ?product ?vendor ?price ?from ?to ?delivery ?webpage(
    If And( ?offer [rdf:type -> bsbm_voc:Offer]
            ?offer [bsbm_voc:product -> ?product]
            ?offer [bsbm_voc:vendor -> ?vendor]
            ?offer [bsbm_voc:price -> ?price]
            ?offer [bsbm_voc:validFrom -> ?from]
            ?offer [bsbm_voc:validTo -> ?to]
            ?offer [bsbm_voc:deliveryDays -> ?delivery]
            ?offer [bsbm_voc:offerWebpage -> ?webpage]
            ?offer [dc:publisher -> ?publisher]
            ?offer [dcc:date -> ?date] )
    Then ?product [bsbm_voc:offerPrice -> ?price] )
      \end{verbatim}
      \caption{The RIF-Core rule inspired by the Berlin SPARQL benchmark.}
      \labelfig{BSBM-rule}
    \end{figure*}

    In order to compare the efficiency of R4 against both Etalis and Sparkwave, we formulated an experiment using the synthetic dataset from the Berlin SPARQL Benchmark \citep{BSBMresults} which was used in the Sparkwave paper.
    We used another 1.1 million triples dataset using the provided data generator, containing information about 100,000 limited-time offers made available by some fictional online marketplace.
    We used a small schema that has 329 product types arranged in a 4-level hierarchy.

>>>>

  \begin{figure*}[t]
    \centering
    \begin{ebnf}
      \Rule{Document}{
              \Optional{\NTerm{IRIMETA}} 
              \Token{Document} 
              \Token{(} 
              \Optional{\NTerm{Base}} 
              \ZeroOrMore{\NTerm{Prefix}} 
              \ZeroOrMore{\NTerm{Import}} 
              \Optional{\NTerm{Group}} 
              \Token{)}
      }
      \Rule{Base}{
              \Token{Base} 
              \Token{(} 
              \NTerm{ANGLEBRACKIRI} 
              \Token{)}
      }
      \Rule{Prefix}{
              \Token{Prefix} 
              \Token{(} 
              \NTerm{Name} 
              \NTerm{ANGLEBRACKIRI} \Token{)}
      }
      \Rule{Import}{
              \Optional{\NTerm{IRIMETA}} 
              \Token{Import} 
              \Token{(} 
              \NTerm{LOCATOR} 
              \Optional{\NTerm{PROFILE}} 
              \Optional{\NTerm{Window}} 
              \Token{)}
      }
      \Rule{Group}{
              \Optional{\NTerm{IRIMETA}} 
              \Token{Group} 
              \Token{(} 
              \ZeroOrMore{\OrList{\NTerm{RULE} \OrSep \NTerm{Group}}} 
              \Token{)}
      }
      \Rule{RULE}{
              \Optional{\NTerm{IRIMETA}}
              \Token{Forall}
              \OneOrMore{\NTerm{Variable}}
              \Token{(}
              \NTerm{CLAUSE}
              \Token{)}
      }
      \OrRule{
              \NTerm{CLAUSE}
      }
      \Rule{CLAUSE}{
              \OrList{\NTerm{Implies} \OrSep \NTerm{ATOMIC}}
      }
      \Rule{Implies}{
              \Optional{\NTerm{IRIMETA}}
              \OrList{\NTerm{ATOMIC} \OrSep \Token{And} \Token{(} \ZeroOrMore{ATOMIC} \Token{)}}
              \Token{:-}
              \NTerm{FORMULA}
      }
      \Rule{LOCATOR}{
              \NTerm{ANGLEBRACKURI}
      }
      \Rule{PROFILE}{
              \NTerm{ANGLEBRACKURI} 
      }
      \Rule{Window}{
              \NTerm{Number}
              \NTerm{TimeUnit}
      }
      \Rule{TimeUnit}{
              \OrList{\Token{ms} \OrSep \Token{s} \OrSep \Token{m} \OrSep \Token{h}}
      }
    \end{ebnf}
    \caption{Streaming RIF-Core Grammar}
    \labelfig{lst-S-RIF-Core}
  \end{figure*}

  A rule document containing any number of rules is submitted to the system.
  We have chosen RIF-Core to be the language in which rules can be represented, because it is compatible with RDF and other semantic web standards, as well as sharing the semantics of positive Datalog.
  The rule document specifies any domain-specific rules as well as an entailment regime \emph{if any} for background reasoning.
  We have also added a simple extension to RIF-Core (in line with the extension of Datalog described in \refsec{semantics}) that enables users to specify a window range as part of their rule set, as shown in \reffig{lst-S-RIF-Core}.
  Further, we propose the extension of the set of `PROFILE's that describe the `Import's of a rule set to include those definitions of RDF streams recognised by the W3C.

@@

\begin{nestedsection}{Evaluation, Results and Discussion}{evaluation}
  To evaluate the performance of R4, we compare it with state-of-the-art systems that provide the capability of performing background reasoning to some extent on streamed semantic data.
  These include Etalis \citep{EP-SPARQL}, Sparkwave \citep{sparkwave}, Streaming knowledge bases \citep{walavalkar08streamingkb}, and the incremental reasoner presented in \citep{inc-reasoning-background-knowledge}.
  To the best of our knowledge, the latter two implementations were never made public, so we compare R4 against Etalis and Sparkwave only.

  \begin{nestedsection}{Methodological Considerations}
    Following the development of semantic stream processors, a number of benchmarks have emerged to test their performance: SRBench\citep{SRBench}, LSBench\citep{linkedstreamproc}, CSRBench and CityBench\citep{ali15}. While these benchmarks provide rich datasets, they mostly do not consider reasoning; with the exception of SRBench, none of the other benchmarks' queries require inference capabilities.

    One of the most important measures of any stream processing system is the maximum input throughput, defined in \citep{scharrenbach13} as the number of data elements in the input stream consumed by the system per time unit; we use this as the key performance indicator in our comparative evaluation of the three systems.
  \end{nestedsection}

  \begin{nestedsection}{Methodology}
   The experiments were performed on an Intel Core i5 computer running at 3.2 GHz with 8 GB memory.  We set up Jtalis (the Java wrapper of Etalis) over SWI-Prolog v7.2.1 and installed Sparkwave v0.5.1.

We followed the experimentation strategy used by Sparkwave , using a synthetic dataset generated with the Berlin SPARQL Benchmark\citep{BSBMresults} containing 1.1 million triples (representing 100,000 limited-time offers made available by an online marketplace). For the background knowledge, we generated a small schema that described 329 product types arranged in a 4-level hierarchy.
